Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-03-16 introduction/Subsections/Introduction.tex
Updates from Overleaf

>>>>

%%%%%%%%%%%%%%%%%%

\begin{figure}[!ht]
\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
\caption{Small excerpt of \textit{Wandrers Nachtlied, Op. 4, D. 224} by Franz Schubert. We can see the passage's original score and the schenkerian unfolding.}
\label{fig:timeseries}
\end{figure}

\begin{figure}[!ht]
\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/schubert.png}% 
\caption{\textit{Wandrers Nachtlied, Op. 4, D. 224} by Franz Schubert as performed by Dietrich Fischer-Dieskau and Jörg Demus}
\label{fig:timeseries}
\end{figure}

\begin{figure}[!ht]
\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/subert redu.png}% 
\caption{\textit{Wandrers Nachtlied, Op. 4, D. 224} by Franz Schubert (Schenkerian reduction or unfolding)}
\label{fig:timeseries}
\end{figure}

### 2023-03-16 methods/subsections/test.tex
Updates from Overleaf

On the other hand, the negative samples are created by shuffling and scrambling the original samples while maintaining their production texture. This is achieved using techniques such as random segment selection, time-domain filtering, and frequency-domain masking. The goal is to maintain the production texture of the samples while disrupting their underlying composition.

@@

%Single
\input{figures/Figures CNN/Single Neuron}
%NN
\input{figures/Figures CNN/Network_graph}

%Backpropagation
\input{figures/Figures CNN/Multi-layer_NN}

%CNN
A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details on the number of channels or neurons per layer or the input data size can be seen in XXX.
\input{figures/Figures CNN/CNN_diagram}

%Single CNN
\input{figures/Figures CNN/Single_CNN}

%Single pooling layer
\input{figures/Figures CNN/Single_Pooling_Layer}

%Backpropagation
\input{figures/Figures CNN/Back_propagation}

>>>>

On the other hand, the negative samples are created by shuffling and scrambling the original samples while maintaining their production texture. This is achieved using random segment selection, time-domain filtering, and frequency-domain masking. The goal is to maintain the production texture of the samples while disrupting their underlying composition.

@@

%Single
\input{figures/cnn/Single Neuron}
%NN
\input{figures/cnn/Network_graph}

%Backpropagation
\input{figures/cnn/Multi-layer_NN}

%CNN
A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details on the number of channels or neurons per layer or the input data size can be seen in XXX.
\input{figures/cnn/CNN_diagram}

%Single CNN
\input{figures/cnn/Single_CNN}

%Single pooling layer
\input{figures/cnn/Single_Pooling_Layer}

%Backpropagation
\input{figures/cnn/Back_propagation}

### 2023-03-16 results/results.tex
Updates from Overleaf

This is an example paragraph. As you can see, the main text uses a font size of 12 pt and a line spacing of 1.5. Neither the paragraphs nor the first lines of paragraphs should be indented.

There is no very strict page limit. Your number of pages will be strongly influenced by the size and total number of your figures and tables. It is recommended staying within 30-50 pages. Do not try to fill as many pages as you can. Longer theses are not necessarily of higher quality and of more non-redundant content than shorter theses. Certainly, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.

@@

This is an example paragraph. As you can see, the main text uses a font size of 12 pt and a line spacing of 1.5. Neither the paragraphs nor the first lines of paragraphs should be indented.

There is no very strict page limit. Your number of pages will be strongly influenced by the size and total number of your figures and tables. It is recommended staying within 30-50 pages. Do not try to fill as many pages as you can. Longer theses are not necessarily of higher quality and of more non-redundant content than shorter theses. Certainly, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.

\begin{figure}[!ht]
\includegraphics[clip,width=\columnwidth]{Figures/PlotTimeSeriesResult}% 
\caption{This is an example of a figure and its caption.}
\label{fig:timeseries}
\end{figure}

>>>>

XXXXXXXXXXXXXXXXX

@@

XXXXXXXXXXXXXXXXX

\begin{figure}[!ht]
\includegraphics[clip,width=\columnwidth]{figures/PlotTimeSeriesResult}% 
\caption{This is an example of a figure and its caption.}
\label{fig:timeseries}
\end{figure}
